Capturing Policies for BYOD

### 2016-10-25 paper.tex
Added a bit on app selection

@@

\newenvironment{policyrule}[1]{%
  \begin{framed}
      \noindent\textbf{\sffamily #1}:~\itshape
}{
  \end{framed}
}

@@

The policies are summarised in \autoref{tab:summary}.
Each policy contains a series of \emph{rules}, which are implemented by one or more \emph{AppPAL assertions}.
The \emph{policy coverage} represents the number of rules that have an AppPAL description attached.
Not all the rules in a policy require an AppPAL translation.
For example rule 9.1 in the NHS policy states:
\begin{policyrule}{NHS}
  Downloading of personal apps onto a corporately issued mobile device should be avoided where possible. 
  The Trust would not encourage staff members to download apps for personal use onto a corporately issued mobile device.
  All staff are reminded that they must adhere to the guidance outlined in the Social Media Policy.
\end{policyrule}
The rule does not prohibit any action, and doesn't require the staff to do anything different.
It does remind staff to be aware of a rule which we could implement with an acknowledegement; a statement that the party has acknowledged a rule.
\begin{lstlisting}
'nhs-trust' says Staff:S mustAcknowledge('avoid-installing-personal-apps').
'nhs-trust' says Staff:S mustAcknowledge('social-media-policy').
\end{lstlisting}
In this case, however, since nothing is required even an acknowledgement seems excessive.

>>>>

\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

@@

\newenvironment{policyrule}[1]{%
  \begin{framed}\footnotesize
      \noindent\textbf{\sffamily #1}:~\itshape%
}{%
  \end{framed}
}

@@

The policies are summarised in \autoref{tab:summary}.
Each policy contains a series of \emph{rules}, which are implemented by one or more \emph{AppPAL assertions}.
The \emph{policy coverage} represents the number of rules that have an AppPAL description attached.

Not all the rules in a policy require an AppPAL translation.
For example rule 9.1 in the NHS policy states:
\begin{policyrule}{NHS}
  Downloading of personal apps onto a corporately issued mobile device should be avoided where possible.
  The Trust would not encourage staff members to download apps for personal use onto a corporately issued mobile device.
  All staff are reminded that they must adhere to the guidance outlined in the Social Media Policy.
\end{policyrule}
The rule does not prohibit any action, and doesn't require the staff to do anything different.
It does remind staff to be aware of a rule which we could implement with an acknowledegement; a statement that the party has acknowledged a rule.
\begin{lstlisting}
'nhs-trust' says Staff:S mustAcknowledge('avoid-installing-personal-apps').
'nhs-trust' says Staff:S mustAcknowledge('social-media-policy').
\end{lstlisting}
In this case, however, since nothing is required even an acknowledgement seems excessive.

Table~\ref{tab:byod-predicates} summarises the facts used by multiple policies.
This shows what concerns and controls and are shared between different BYOD policies.
All five of the policies make use of acknowledgements, for example.
This could be because not all the rules in a policy can be enforced through technical means, 
  or it could indicate policy authors care more that the subjects are aware of the rules than they do for rigorous enforcement.
All but the HiMMS policy have rules that include locking down a device by disabling features.
All but the Edinburgh policy have rules that look at what should happen when a device is lost,
  and have rules that require employees inform someone when something happens.
These common concerns suggest where future \ac{MDM} software should focus their efforts.

Only the NHS and SANS, the two most complex policies, describe when a device can install an app and what kinds of apps are installable.
In both policies this is predominantly limited to a delegation to the appropriate groups to authorize an app.
For example, in the SANS policy the IT-Department are responsible for deciding what apps can be installed.
\begin{policyrule}{SANS}
  The IT Department maintains lists of allowed and unauthorized applications and makes them available to users on the intranet.
  \normalfont
  \begin{lstlisting}
'company' says 'it-department' can-say App:A isInstallable.
  \end{lstlisting}
\end{policyrule}
The NHS policy, however, is significantly more complicated.
Apps have to be approved by three different groups (the Integrated Governance Comitee, the Employee's manager, and the relevant group within the trust depending on where the employee works) before the trust will say that an app can be installed.
\begin{policyrule}{NHS}
  Apps for work usage must not be downloaded onto corporately issued
  mobile devices (even if approved on the NHS apps store) unless they have
  been approved through the following Trust channels:

  Clinical apps; at the time of writing there are no apps clinically
  approved by the Trust for use with patients~/~clients. However, if a
  member of staff believes that there are clinical apps or other
  technologies that could benefit their patients~/~clients, this should be
  discussed with the clinical lead in the first instance and ratification
  should be sought via the Care and Clinical Policies Group. A clinical
  app should not be used if it has not been approved via this group.

  Business apps; at the time of writing there are no business (i.e.,
  non-clinical) apps approved by the Trust for use other than those
  preloaded onto the device at the point of issue. However, if a member of
  staff believes that there are apps or other technologies that could
  benefit their non-clinical work, ratification of the app must be sought
  via the Management of Information Group (MIG). An app should not be used
  if it has not been approved via this group.

  Following approval through Care and Clinical Policies and~/~or MIG, final
  approval will be required through Integrated Governance Committee.

  Use of paid apps must be agreed in advance with the device holder's line
  manager and there should be a demonstrable benefit.
  \normalfont
  \begin{lstlisting}
'nhs-trust' says App isInstallable if App hasMet('clinical-use-case').
'nhs-trust' says App isInstallable if App hasMet('business-use-case').
'nhs-trust' says 'cacpg' can-say App:A hasMet('clinical-use-case').
'nhs-trust' says 'mig' can-say App:A hasMet('business-use-case').
'nhs-trust' says App isInstallable
  if App hasMet('final-app-approval').
'nhs-trust' says 'igc' can-say App hasMet('final-app-approval').
'nhs-trust' says Device canInstall(App)
  if App isInstallable,
     App isApprovedFor(Device).
'nhs-trust' says Employee:Manager can-say
  App:A isApprovedFor(Device)
  if Manager isResponsibleFor(Device).
  \end{lstlisting}
\end{policyrule}
Given that user's have privacy preferences expressable as permissions~\cite{lin_modeling_2014}, we might expect corporate policies to also express preferences about what permissions an app can have.
This does not appear to be the case, however. 
As part of selecting the apps an IT department or group may chose to use advanced instrumentation and policies~\cite{armando_enabling_2014}, or they may manually chose apps to form a curated app store as some \ac{MDM} vendors allow.
But from the perspective of the policy itself it is more important \emph{who} makes the decision rather than \emph{what} they chose, if they have an opinion at all.

\begin{table}\centering\footnotesize
  \newcommand{\angledtitle}[1]{\rlap{\rotatebox{30}{#1}}}
  \sffamily
  \begin{tabular}{l c c c c c p{0.45\linewidth} }
    \toprule
    Predicate                                   & \angledtitle{Sirens}   & \angledtitle{Edinburgh} & \angledtitle{HiMMS} & \angledtitle{NHS} & \angledtitle{SANS}
    & Description                                                                          \\
    \midrule
    Device \texttt{canBackupTo}(Server)         &                        & \cmark                  & \cmark              &                   &
    & Says the device may send backups to a server.                                        \\
    Device \texttt{canCall}(Number)             &                        &                         &                     & \cmark            & \cmark
    & Says the telephone numbers a device can call.                                        \\
    Device \texttt{canConnectToAP}(AP)          &                        &                         & \cmark              &                   & \cmark
    & Says a device may associate with an access point.                                    \\
    Device \texttt{canConnectToNetwork}(Subnet) & \cmark                 &                         &                     &                   & \cmark
    & Says the device may connect to a network, for example computers all within a subnet. \\
    Device \texttt{canConnectToServer}(IP)      &                        &                         &                     & \cmark            & \cmark
    & Says the subject (a device) can connect to a given server (identitfied by a URL).    \\
    Device \texttt{canInstall}(App)             &                        &                         &                     & \cmark            & \cmark
    & Says the device may install an app.                                                  \\
    User \texttt{canMonitor}(Device)            & \cmark                 &                         &                     & \cmark            & \cmark
    & Says the subject (a user) can monitor and unlock a device.                           \\
    Device \texttt{canStore}(File)              &                        &                         & \cmark              &                   & \cmark
    & Says a device may store some data in permanent (non-transient) storage.              \\
    User \texttt{canUse}(Device)                &                        &                         &                     & \cmark            & \cmark
    & Says a user may use a device.                                                        \\
    User \texttt{hasAcknowledged}(Policy)       & \cmark                 & \cmark                  & \cmark              & \cmark            & \cmark
    & Says an individual has acknoweldged a policy.                                        \\
    Device \texttt{hasFeature}(Feature)         &                        & \cmark                  &                     & \cmark            &
    & Says a device has a feature enabled.                                                 \\
    Something \texttt{hasMet}(Policy)           &                        & \cmark                  &                     & \cmark            & \cmark
    & Says a something has met a given set of requirements.                                \\
    Device \texttt{isActivated}                 &                        &                         & \cmark              & \cmark            & \cmark
    & Specifies a device has been activated for BYOD usage.                                \\
    App \texttt{isApp}                          & \cmark                 &                         & \cmark              & \cmark            & \cmark
    & Specifies an app.                                                                    \\
    Something \texttt{isApproved}               &                        &                         & \cmark              &                   & \cmark
    & Specifies that something has been vetted and approved of.                            \\
    Data \texttt{isData}                        & \cmark                 &                         &                     &                   & \cmark
    & Specifies data.                                                                      \\
    Device \texttt{isDevice}                    & \cmark                 & \cmark                  & \cmark              & \cmark            & \cmark
    & Specifies a device.                                                                  \\
    User \texttt{isEmployee}                    & \cmark                 & \cmark                  &                     & \cmark            & \cmark
    & Specifies that someone is an employee.                                               \\
    Device \texttt{isEncrypted}                 &                        & \cmark                  &                     & \cmark            & \cmark
    & Specifies a device is encrypted.                                                     \\
    Feature \texttt{isFeature}                  & \cmark                 &                         &                     &                   & \cmark
    & Specifies a feature.                                                                 \\
    App \texttt{isInstallable}                  &                        &                         &                     & \cmark            & \cmark
    & Specifies an app is installable.                                                     \\
    Device \texttt{isLost}                      & \cmark                 &                         & \cmark              & \cmark            & \cmark
    & Specifies a device is missing.                                                       \\
    Device \texttt{isOwnedBy}(User)             & \cmark                 & \cmark                  & \cmark              & \cmark            & \cmark
    & Specifies something's owner.                                                         \\
    File \texttt{isSecurityLevel}(Level)        &                        &                         & \cmark              &                   & \cmark
    & Specifies some data as having business sensitive information.                        \\
    Something \texttt{isString}                 & \cmark                 &                         &                     & \cmark            &
    & Specifies a string.                                                                  \\
    Number \texttt{isTelephoneNumber}           &                        &                         &                     & \cmark            & \cmark
    & Specifies a telephone number.                                                        \\
    Device \texttt{mustDisable}(Feature)        & \cmark                 & \cmark                  &                     & \cmark            & \cmark
    & Forces the disablement of a feature (or a device).                                   \\
    User \texttt{mustInform}(User, Something)   & \cmark                 &                         & \cmark              & \cmark            & \cmark
    & Forces someone to disclose something to someone.                                     \\
    Device \texttt{mustWipe}                    & \cmark                 &                         & \cmark              & \cmark            &
    & Forces a device to be erased.                                                        \\
    \bottomrule
  \end{tabular}
  \caption{Summary of AppPAL facts used in multiple BYOD policies.}
  \label{tab:byod-predicates}
\end{table}
